### 2010-01-29 pkg/yuimadocs/inst/doc/yuima_4.Rnw
minor fix
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@62 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Terminal <- 1
p1 <- 0.2
p2 <- 0.3
rate<-c(p1, p2)
n <- 1000 
# Change to n<-1000
division <- 1200
# Change too division <- 1200

yuima.samp <- setSampling(Terminal=Terminal,division=division)
yuima <- setYuima(model=cor.mod, sampling=yuima.samp)

@@

\begin{thebibliography}{99}
\bibitem{hay-yos05}
Hayashi, T., Yoshida, N.: 
On Covariance Estimation of Non-synchronously Observed Diffusion Processes. 
Bernoulli, {\bf 11}, 2, 359-379 (2005)

\bibitem{hay-yos04}
Hayashi, T., Yoshida, N.: 
Asymptotic normality of a covariance estimator for nonsynchronously observed diffusion processes. 
Annals of the Institute of Statistical Mathematics, 
{\bf 60}, 2, %/ 2008”N6ŒŽ 
367-406 (2008)

\bibitem{hay-yos06}
Hayashi, T., Yoshida, N.: 
Nonsynchronous Covariance Estimator and Limit Theorem. 
Research Memorandum No.1020, Institute of Statistical Mathematics, 2006

\bibitem{hay-yos08}
Hayashi, T., Yoshida, N.: 
Nonsynchronous Covariance Estimator and Limit Theorem II. 
Research Memorandum No.1067, Institute of Statistical Mathematics, 2008

\end{thebibliography}

>>>>

Terminal <- 1
p1 <- 0.2
p2 <- 0.3
rate<-c(p1, p2)
n <- 1000 
# Change to n<-1000
n <- 1200
# Change too n <- 1200

yuima.samp <- setSampling(Terminal=Terminal,n=n)
yuima <- setYuima(model=cor.mod, sampling=yuima.samp)

@@
